The transition redshift as a probe of reionization

### 2019-08-13 paper/ms.tex
Touch up detectability section

The variance of the cross-spectrum between the 21~cm field and a line $i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
\beq \label{eq:var_xps}
\text{Var}\left[P_{21,i}\right] = P_{21,i}^2 + P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
\eeq
where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
noise contribution, and is similarly defined for $P_{i,\text{tot}}$.

>>>>

The variance of the cross-spectrum between the 21~cm field and a line $i$ is
given by \citep[e.g.][]{2007ApJ...660.1030F}
\beq \label{eq:var_xps}
\Var{P_{21,i}} = P_{21,i}^2 + 
                                  P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
\eeq
where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
noise contribution. $P_{i,\text{tot}}$ is defined similarly.

By expanding $P_{21,i}$ as a linear function about \zst{}, we can estimate the
error on \zst{} by
\beq \label{eq:error_on_zst}
\Var{\zst} = \left(\left.\frac{\partial P_{21,i}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,i}}
\eeq
